### 2022-03-22 paper/output/document/thesis_4_applications.tex
finished another read thrgh

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this chapter, I demonstrate that my system can produce correct judgements for challenging moral 
dilemmas that naive ethical reasoning cannot satisfactorily handle. Because my system is faithful to
philosophical literature, it can reproduce complex ethical judgements presented by philosophers as 
solutions to controversial open questions in ethics.
These dilemmas serve as examples of how my system could be used
in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
than those presented in Chapter \ref{details}. Moreover, in the process of formalizing these dilemmas, 
I isolated the exact conditon that makes a maxim about lying wrong, an insight that could contribute to 
the philosophical literature on lying.

@@

In this chapter, I tackle this challenge by
endowing my system with this kind of common sense in the specific case of lying. My system needs common 
sense facts and definitions because, while it has the ability to reason
using the Formula of Universal Law, this reasoning must be applied to objects that are defined
using common sense. Because these common sense facts can determine my system's judgements, they are part of the trusted
code base for my system, or the logic and code that a user must trust in order to trust my system. 
Changing these common sense facts will change the judgements 
that my system makes. For example, if we define truth telling as an act that is self-contradictory (perhaps
by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
Malicious common sense facts and definitions will result in bad ethical judgements. 
The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
system, and virtually all prior attempts in machine ethics face similar challenges. Many prior attempts
sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.

This chapter will provide examples of the kinds of common sense facts required to get my system
off the ground. I use a lean and uncontroversial common sense database
to achieve robust and powerful results. This serves as evidence for the ease of automating
Kantian ethics, an example of the additional work required to use my system in practice, and a 
demonstration of my system's power and flexibility. These examples demonstrate that, armed with nuanced 
common sense facts, my system can make sophisticated judgements faithful to philosophical literature.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lies and Jokes \label{joking}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The moral status of lying is hotly debated in the Kantian literature. I focus on two dilemmas
presented in Korsgaard's ``Right to Lie,'' which 
examines Kant's prohibition on lying \citep{KorsgaardRTL}. She begins with the case of 
lying and joking. Many of Kant's critics argue that his prohibition on lies includes lies told in 
the context of a joke, which should be permissible. Korsgaard responds by arguing 
that there is a crucial difference between lying and joking: lies involve deception, but jokes do not. 
The purpose of a joke is amusement, which does not rely on the listener believing the story told. 
Given appropriate definitions of lies and jokes, my system shows that jokes are permissible but lies 
are not, demonstrating its power and flexibility. This section demonstrates how my system can be used 
in practice; it needs to be given some baseline common sense facts, but with those facts, it can make 
sophisticated judgements. Moreover, because my system is faithful to definitions found in philosophical 
literature, it can perform nuanced reasoning, demonstrating the value of faithful automated ethics.

@@

Using the above definitions, I define lying. I characterize a maxim as involving a lie if 
the act requires knowingly uttering a falsehood and the end requires that some person $p$ believe 
the false statement $t$.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ lie{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}lie\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{The abbreviation above maps a maxim to a boolean value that indicates if it is a lie.%
}%
\begin{isamarkuptext}%
To avoid unintentional wrongdoing, I focus on ``knowing lies,'' 
in which the speaker is aware that they are lying. It is uncontroversial that, in order for an act to be
a knowing lie, the speaker must utter a false statement that they do not believe. This also makes it 
easier to make moral judgements about the speaker's action, since they were, at the very least, aware
of their lie. The second half of
this definition requires that the goal of the lie is deception. This is inspired by  Korsgaard's interpretation 
of a lie. She understands a lie as a kind of falsehood that is usually effective \emph{because} it decieves
\citep[4]{KorsgaardRTL}. In my formalization, this means that the purpose or goal of the maxim must
involve decieving someone, or, in other words, that someone believe what the speaker knows to be a 
falsehood.

@@

common sense background is a direct formalization of the premises of Korsgaard's argument. Using these
relatively minimal premises about individual behavior, my system derives a prohibition against lying.%

@@

trust'' fact. In the rest of this section, I will test versions of this assumption, effectively encoding 

@@

Now that I have formalized Korsgaard's argument for why lying is prohibited, I will
implement her argument for why jokes are permissible. Specifically, she defines a joke as a story that is 
false and argues that joking is permissible because ``the universal practice of lying in the context of jokes
does not interfere with the purpose of jokes, which is to amuse and does not depend on
deception'' \citep[4]{KorsgaardRTL}. I use the fact that a joke does not depend on deception as the 
defining feature of a joke.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ joke{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}joke\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ \ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Thie abbreviation states that a maxim is a joke if the action involves knowingly uttering a falsehood but
the goal does \emph{not} require that someone believe the falsehood told.%
}%
\begin{isamarkuptext}%
This definition of a joke defines a joke as a falsehood uttered for some purpose that 
doesn't require deception, where deception involves someone believing the uttered falsehood. 
This definition doesn't require any conception of humor, but merely
distinguishes jokes from lies.

@@

There are two implications of this section. First, my system is capable of performing ethical reasoning
sophisticated enough to show that lying is prohibited but joking is not. This is a direct consequence 
of my system's use of a robust conception of a maxim, which encodes the goal of an act as part of the 
maxim being evaluated. Because my implementation is faithful to philosophical literature, it is able 
to recreate Korsgaard's solution to a complex ethical dilemma that philosophers debated for decades. Second, 
in the process of making this argument precise, my system isolated a necessary and sufficient condition 
of a maxim about uttering a falsehood being prohibited: that the goal require that someone believe
the falsehood. This condition made an long-standing argument in Kantian ethics more precise, can guide 
the correct formulation of future maxims, and could contribute to the rich philosophical conversation
about the wrongness of lying. In other words, an insight generated by the
computer provides value to ethicists, bolstering the argument for computational ethics provided in 
Section \ref{computationalethics}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lying to a Liar \label{murderer}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
My system can not only distinguish between lying and joking, but it can also resolve the paradox of 
the murderer at the door. In this dilemma, murderer Bill knocks on your door asking about Sara, his 
intended victim. Sara is at home, but moral intuition says that you should lie to Bill and say 
that she is out to prevent him from murdering her. Many critics of Kantian ethics argue that the 
FUL prohibits you from lying in this instance; if everyone lied to murderers, then murderers wouldn't 
believe the lies and would search the house anyways. Korsgaard resolved this centuries-long debate by 
noting that the maxim of lying to a murderer is actually that of lying to a liar: Bill cannot 
announce his intentions to murder; instead, he must ``must suppose that you do not know who he is 
and what he has in mind'' \citep{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will 
lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5, 
she accepts that her arguments will not apply in the case of the honest murderer 
who announces his intentions, so she restricts her focus to the case of lying to a liar. She claims 
that in the case of the honest murderer, the correct act is to refuse to respond. Since I am formalizing
Korsgaard's argument, I also accept this assumption.} Thus, the maxim 
in question specifies that when someone lies to you, you are allowed to lie to them. The maxim of 
lying to the murderer is actually the maxim of lying to a liar, which is permissible.

@@

intention, he is implicitly telling you that he is not a murderer, as people normally assume that 

@@

these kinds of judgements demonstrate that, with additional work, my system could be used in practice 

@@

%:%80=52%:%
%:%81=53%:%
%:%82=54%:%
%:%91=57%:%

@@

%:%122=79%:%
%:%123=80%:%

@@

%:%126=84%:%
%:%127=84%:%
%:%129=85%:%
%:%130=86%:%
%:%131=87%:%

@@

%:%138=93%:%
%:%139=94%:%

@@

%:%142=98%:%
%:%143=98%:%
%:%145=99%:%
%:%146=100%:%
%:%147=100%:%
%:%148=101%:%
%:%149=101%:%
%:%150=102%:%
%:%152=103%:%
%:%153=103%:%
%:%154=104%:%
%:%155=104%:%
%:%156=105%:%

@@

%:%160=108%:%
%:%161=109%:%
%:%162=110%:%

@@

%:%172=121%:%

@@

%:%174=123%:%
%:%176=125%:%
%:%177=125%:%
%:%178=126%:%
%:%180=127%:%

@@

%:%193=139%:%

@@

%:%195=141%:%
%:%197=143%:%
%:%198=143%:%
%:%200=144%:%
%:%201=145%:%
%:%202=146%:%
%:%203=146%:%
%:%204=147%:%
%:%205=147%:%
%:%207=148%:%
%:%208=149%:%
%:%209=149%:%
%:%210=150%:%
%:%211=150%:%
%:%213=151%:%
%:%216=153%:%

@@

%:%218=155%:%
%:%219=156%:%
%:%221=158%:%
%:%222=158%:%
%:%223=159%:%
%:%224=160%:%
%:%226=161%:%
%:%227=161%:%
%:%228=162%:%
%:%230=163%:%
%:%231=164%:%
%:%232=164%:%
%:%233=165%:%

@@

%:%237=168%:%
%:%238=169%:%
%:%239=170%:%
%:%240=171%:%
%:%241=171%:%
%:%242=172%:%
%:%244=173%:%
%:%245=173%:%
%:%246=174%:%
%:%253=175%:%
%:%254=175%:%
%:%255=176%:%
%:%256=176%:%
%:%257=177%:%
%:%258=177%:%
%:%260=178%:%
%:%261=179%:%
%:%262=180%:%
%:%263=181%:%
%:%264=181%:%
%:%265=182%:%
%:%266=182%:%
%:%267=183%:%
%:%268=183%:%
%:%269=184%:%
%:%270=184%:%
%:%271=185%:%
%:%272=185%:%
%:%273=185%:%
%:%275=186%:%
%:%276=187%:%
%:%277=187%:%
%:%278=188%:%

@@

%:%299=201%:%

@@

%:%301=203%:%
%:%302=204%:%
%:%304=206%:%
%:%305=206%:%
%:%306=207%:%
%:%308=208%:%
%:%309=209%:%

@@

%:%317=216%:%

@@

%:%319=218%:%
%:%320=219%:%
%:%322=221%:%
%:%323=221%:%
%:%324=222%:%
%:%325=223%:%
%:%327=224%:%
%:%328=224%:%
%:%329=225%:%
%:%331=226%:%
%:%332=227%:%
%:%333=227%:%
%:%334=228%:%
%:%336=229%:%
%:%337=229%:%
%:%338=230%:%
%:%340=231%:%
%:%341=231%:%
%:%342=232%:%
%:%345=233%:%
%:%349=233%:%
%:%350=233%:%

@@

%:%353=235%:%
%:%354=236%:%
%:%355=237%:%
%:%356=238%:%

@@

%:%420=289%:%
%:%432=292%:%

@@

%:%452=312%:%
%:%453=312%:%
%:%455=313%:%
%:%456=313%:%

@@

%:%458=314%:%
%:%460=315%:%

@@

%:%463=317%:%

@@

%:%465=318%:%
%:%467=319%:%
%:%468=319%:%

@@

%:%470=320%:%
%:%472=321%:%
%:%473=321%:%

@@

%:%475=322%:%

@@

%:%478=324%:%

@@

%:%482=327%:%

@@

%:%487=332%:%
%:%488=332%:%
%:%490=333%:%
%:%491=333%:%

@@

%:%493=334%:%

@@

%:%496=336%:%
%:%497=336%:%

@@

%:%499=337%:%
%:%501=338%:%
%:%502=338%:%

@@

%:%504=339%:%

@@

%:%507=341%:%

@@

%:%524=374%:%

@@

%:%534=384%:%
%:%535=384%:%

@@

%:%539=387%:%
%:%540=387%:%

@@

%:%543=389%:%
%:%544=389%:%

@@

%:%547=391%:%

@@

%:%552=395%:%

@@

%:%555=397%:%

@@

%:%562=403%:%

@@

%:%565=405%:%

@@

%:%567=406%:%

@@

%:%571=408%:%
%:%575=408%:%
%:%576=408%:%
%:%577=408%:%
%:%579=409%:%

@@

%:%591=413%:%

@@

%:%596=418%:%
%:%597=418%:%

@@

%:%600=420%:%
%:%601=420%:%

@@

%:%604=422%:%
%:%605=422%:%

@@

%:%608=424%:%
%:%609=424%:%

@@

%:%612=426%:%
%:%613=426%:%

@@

%:%616=428%:%

@@

%:%618=429%:%

@@

%:%626=431%:%
%:%627=431%:%

@@

%:%629=432%:%

@@

%:%631=433%:%
%:%632=433%:%

@@

%:%634=434%:%

@@

%:%636=435%:%
%:%637=435%:%

@@

%:%639=436%:%

@@

%:%641=437%:%
%:%642=437%:%

@@

%:%653=440%:%

@@

>>>>

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this chapter, I demonstrate that my system can produce sophisticated judgements for challenging moral 
dilemmas that naive Kantian ethical reasoning cannot satisfactorily handle. Because my system is faithful to
philosophical literature, it can reproduce complex ethical judgements presented by philosophers as 
solutions to controversial open questions in ethics. These dilemmas serve as examples of how my system could be used
in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
than those presented in Chapter \ref{details}. Moreover, in the process of formalizing these dilemmas, 
I isolate the exact conditon that makes a maxim about lying wrong, an insight that could contribute to 
the philosophical literature on lying.

@@

In this chapter, I tackle this challenge by endowing my system with this kind of common sense in the 
specific case of lying. While my system has the ability to reason
using the Formula of Universal Law, this reasoning must be applied to objects that are defined
using common sense. Because common sense facts can determine my system's judgements, they are part of the trusted
code base for my system, or the logic and code that a user must trust in order to trust my system. 
Malicious common sense facts will result in bad judgements.
For example, if we define truth telling as an act that is self-contradictory (perhaps
by defining it as $p \wedge \neg p$), then my system will output that truth telling is prohibited.
The challenge of endowing automated ethical reasoners with common sense reasoning is not unique to my 
system, and virtually all prior attempts in machine ethics face similar challenges. Many prior attempts
sidestep this question, whereas I contribute an prototype implementation of one kind of common sense reasoning.

This chapter will provide examples of the kinds of common sense facts required to get my system
off the ground. I use a lean and uncontroversial common sense database
to achieve robust and powerful results. This serves as evidence for the ease of automating
Kantian ethics, an example of the additional work required to use my system in practice, and a 
demonstration of my system's power and flexibility. These examples demonstrate that, armed with some basic 
common sense facts, my system can make sophisticated judgements faithful to philosophical literature.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lies and Jokes \label{joking}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The moral status of lying is hotly debated in the Kantian literature. I focus on two dilemmas
presented in Korsgaard's ``Right to Lie,'' which 
examines Kant's prohibition on lying \citep{KorsgaardRTL}. She begins with the case of 
lying and joking. To demonstrate that Kant's theory is too demanding, many of his critics argue that 
his prohibition on lies includes lies told in the context of a joke, which should be permissible. Korsgaard responds by arguing 
that there is a crucial difference between lying and joking: lies involve deception, but jokes do not. 
The purpose of a joke is amusement, which does not rely on the listener believing the story told. 
Given appropriate definitions of lies and jokes, my system shows that jokes are permissible but lies 
are not, demonstrating its power and flexibility. This section demonstrates how my system can be used 
in practice; it needs to be given some baseline common sense facts, but with those facts, it can make 
sophisticated judgements. Moreover, because my system is faithful to definitions found in philosophical 
literature, it can perform nuanced reasoning, demonstrating the value of faithful automated ethics.

@@

Using the above definitions, I define lying. I characterize a maxim as involving a lie if 
the act requires knowingly uttering a falsehood and the end requires that some person $p$ believe 
the false statement $t$.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ lie{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}lie\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{The abbreviation above maps a maxim to a boolean value that indicates if it is a lie.%
}%
\begin{isamarkuptext}%
To avoid issues with unintentional wrongdoing, I focus on ``knowing lies,'' 
in which the speaker is aware that they are lying. This makes it easier to make moral judgements about 
the speaker's action, since they were, at the very least, aware of their lie. It is uncontroversial 
that, in order for an act to be a knowing lie, the speaker must utter a false statement that they do 
not believe. The second half of
this definition requires that the goal of the lie is deception. This is inspired by  Korsgaard's interpretation 
of a lie. She understands a lie as a kind of falsehood that is usually effective \emph{because} it decieves
\citep[4]{KorsgaardRTL}. In my formalization, this means that the purpose or goal of the maxim must
involve decieving someone, or that someone believe what the speaker knows to be a 
falsehood.

@@

common sense background is a direct formalization of the premises of Korsgaard's argument.%

@@

trust'' fact. In the rest of this chapter, I will test another version of this assumption, effectively encoding 

@@

Now that I have formalized Korsgaard's argument for why lying is prohibited, I will
implement her argument for why jokes are permissible. Specifically, she defines a joke as a story that is 
false and argues that joking is permissible because ``the universal practice of lying in the context of jokes
does not interfere with the purpose of jokes, which is to amuse and does not depend on
deception'' \citep[4]{KorsgaardRTL}. I use the fact that a joke does not depend on deception as the 
defining feature of a joke.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ joke{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}joke\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ \ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{Thie abbreviation states that a maxim is a joke if the action involves knowingly uttering a falsehood but
the goal does \emph{not} require that someone believe the falsehood told.%
}%
\begin{isamarkuptext}%
This definition of a joke defines a joke as a falsehood uttered for some purpose that 
doesn't require deception, where deception involves someone believing the uttered falsehood. 
This definition is thin because it doesn't require any conception of humor, but merely
distinguishes jokes from lies.

@@

This demonstrates one kind of philosophical contribution that computational ethics can make: it can 
offer insights that guide the formulation of permissible maxims, as in the surprise party example
above. In Section \ref{computationalethics}, I provide another example of such a boundary condition 
for the formulation of a maxim, which serves as further evidence of the potential of computational ethics.

There are two implications of this section. First, my system is capable of performing ethical reasoning
sophisticated enough to show that lying is prohibited but joking is not. This is a direct consequence 
of my system's use of a robust conception of a maxim, which encodes the goal of an act as part of the 
maxim being evaluated. Because my implementation is faithful to philosophical literature, it is able 
to recreate Korsgaard's solution to a complex ethical dilemma that philosophers debated for decades. Second, 
in the process of making this argument precise, my system isolated a necessary and sufficient condition 
for a maxim about uttering a falsehood to be prohibited: the goal must require that someone believe
the falsehood. This condition made an long-standing argument in Kantian ethics more precise, can guide 
the correct formulation of future maxims, and could contribute to the rich philosophical conversation
about the wrongness of lying. In other words, an insight generated by the
computer could provide value to ethicists, bolstering the argument for computational ethics provided in 
Section \ref{computationalethics}.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Lying to a Liar \label{murderer}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
My system can not only distinguish between lying and joking, but it can also resolve the paradox of 
the murderer at the door. In this dilemma, murderer Bill knocks on your door asking about Sara, his 
intended victim. Sara is at home, but moral intuition says that you should lie to Bill and say 
that she is out to prevent him from murdering her. Many critics of Kantian ethics argue that the 
FUL prohibits you from lying in this instance; if everyone lied to murderers, then murderers wouldn't 
believe the lies and would search the house anyways. Korsgaard resolved this centuries-long debate by 
noting that the maxim of lying to a murderer is actually that of lying to a liar: Bill cannot 
announce his intentions to murder; instead, he must ``must suppose that you do not know who he is 
and what he has in mind'' \citep{KorsgaardRTL}.\footnote{Korsgaard assumes that the murderer will 
lie about his identity in order to take advantage of your honesty to find his victim. In footnote 5, 
she accepts that her arguments will not apply in the case of the honest murderer 
who announces his intentions, so she restricts her focus to the case of lying to a liar. She claims 
that in the case of the honest murderer, the correct act is to refuse to respond. Since I am formalizing
Korsgaard's argument, I also accept this assumption.} Thus, the maxim 
in question specifies that when someone lies to you, you are allowed to lie to them. The maxim of 
lying to the murderer is actually the maxim of lying to a liar, which is permissible.

@@

intention, he is implicitly telling you that he is not a murderer, as people typically assume that 

@@

these examples demonstrate that, with some additional work, my system could be used in practice 

@@

%:%88=54%:%
%:%100=57%:%
%:%101=58%:%
%:%102=59%:%

@@

%:%123=81%:%

@@

%:%126=82%:%
%:%127=83%:%
%:%128=84%:%
%:%131=86%:%
%:%132=87%:%
%:%133=88%:%

@@

%:%139=95%:%

@@

%:%142=96%:%
%:%143=97%:%
%:%144=97%:%
%:%145=98%:%
%:%146=98%:%
%:%147=99%:%
%:%149=100%:%
%:%150=100%:%
%:%151=101%:%
%:%152=101%:%
%:%153=102%:%
%:%155=103%:%
%:%156=104%:%
%:%157=105%:%

@@

%:%162=111%:%
%:%163=112%:%
%:%164=113%:%

@@

@@

%:%174=122%:%
%:%175=123%:%
%:%177=124%:%
%:%180=126%:%
%:%181=127%:%
%:%182=128%:%

@@

@@

%:%195=140%:%
%:%197=141%:%
%:%198=142%:%
%:%199=143%:%
%:%200=143%:%
%:%201=144%:%
%:%202=144%:%
%:%204=145%:%
%:%205=146%:%
%:%206=146%:%
%:%207=147%:%
%:%208=147%:%
%:%210=148%:%
%:%213=150%:%
%:%214=151%:%
%:%215=152%:%

@@

%:%218=154%:%
%:%219=155%:%
%:%220=156%:%
%:%222=157%:%
%:%223=157%:%
%:%224=158%:%
%:%226=159%:%
%:%227=160%:%
%:%228=160%:%
%:%229=161%:%
%:%231=162%:%
%:%232=163%:%
%:%233=164%:%
%:%234=165%:%

@@

%:%237=167%:%
%:%238=168%:%
%:%240=169%:%
%:%241=169%:%
%:%242=170%:%
%:%249=171%:%
%:%250=171%:%
%:%251=172%:%
%:%252=172%:%
%:%253=173%:%
%:%254=173%:%
%:%256=174%:%
%:%257=175%:%
%:%258=176%:%
%:%259=177%:%
%:%260=177%:%
%:%261=178%:%
%:%262=178%:%
%:%263=179%:%
%:%264=179%:%
%:%265=180%:%
%:%266=180%:%
%:%267=181%:%
%:%268=181%:%
%:%269=181%:%
%:%271=182%:%
%:%272=183%:%
%:%273=183%:%
%:%274=184%:%
%:%284=186%:%
%:%285=187%:%
%:%286=188%:%
%:%287=189%:%

@@

@@

%:%301=202%:%
%:%302=203%:%
%:%304=204%:%
%:%305=205%:%
%:%308=207%:%
%:%309=208%:%
%:%310=209%:%
%:%311=210%:%

@@

@@

%:%319=217%:%
%:%320=218%:%
%:%321=219%:%
%:%323=220%:%
%:%324=220%:%
%:%325=221%:%
%:%327=222%:%
%:%328=223%:%
%:%329=223%:%
%:%330=224%:%
%:%332=225%:%
%:%333=225%:%
%:%334=226%:%
%:%336=227%:%
%:%337=227%:%
%:%338=228%:%
%:%341=229%:%
%:%345=229%:%
%:%346=229%:%
%:%348=230%:%
%:%349=231%:%
%:%350=232%:%
%:%351=233%:%

@@

%:%362=237%:%
%:%363=238%:%
%:%364=239%:%
%:%365=240%:%

@@

%:%412=287%:%
%:%421=290%:%

@@

%:%451=311%:%
%:%453=313%:%
%:%454=313%:%
%:%456=314%:%

@@

%:%458=315%:%
%:%459=315%:%

@@

%:%463=318%:%

@@

%:%465=319%:%
%:%466=319%:%
%:%468=320%:%

@@

%:%470=321%:%
%:%471=321%:%
%:%473=322%:%

@@

%:%475=323%:%

@@

%:%477=324%:%

@@

%:%480=326%:%

@@

%:%486=331%:%
%:%488=333%:%
%:%489=333%:%
%:%491=334%:%

@@

%:%493=335%:%

@@

%:%495=336%:%
%:%497=337%:%

@@

%:%499=338%:%
%:%500=338%:%
%:%502=339%:%

@@

%:%504=340%:%

@@

%:%506=341%:%

@@

%:%509=343%:%

@@

%:%533=383%:%
%:%535=385%:%

@@

%:%538=387%:%
%:%540=388%:%

@@

%:%542=389%:%
%:%544=390%:%

@@

%:%546=391%:%

@@

%:%552=396%:%

@@

%:%554=397%:%

@@

%:%562=404%:%

@@

%:%564=405%:%

@@

%:%567=407%:%

@@

%:%569=408%:%
%:%572=409%:%
%:%576=409%:%
%:%577=409%:%
%:%578=409%:%

@@

%:%582=412%:%

@@

%:%595=417%:%
%:%597=419%:%

@@

%:%599=420%:%
%:%601=421%:%

@@

%:%603=422%:%
%:%605=423%:%

@@

%:%607=424%:%
%:%609=425%:%

@@

%:%611=426%:%
%:%613=427%:%

@@

%:%615=428%:%

@@

%:%618=430%:%

@@

%:%620=431%:%
%:%627=432%:%

@@

%:%629=433%:%

@@

%:%631=434%:%
%:%632=434%:%

@@

%:%634=435%:%

@@

%:%636=436%:%
%:%637=436%:%

@@

%:%639=437%:%

@@

%:%641=438%:%
%:%642=438%:%

@@

%:%644=439%:%

@@

%:%689=476%:%
